Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-06 BN_discretizer_paper.tex
check one word

\section{Discretizing Multiple Continuous Variable with Structure Learning}
\label{DMC_SL}
\subsection{Discretization of Multiple Continuous Variables}
\label{DMC}
If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables. While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the lastest iteration. The prediscretization can be done by equal-width discretization, which is defined as follows:
\begin{equation}
M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, \ldots, \delta, max_X \},
\end{equation}
where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$, and $k$ is the desired number of intervals after equal-width discretization. $k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities. After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root). We call one such series of discretizations as a cycle. The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result. For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable. If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of both $P_2$ and $X$. However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.

>>>>

\section{Discretizing Multiple Continuous Variable with Structure Learning}
\label{DMC_SL}
\subsection{Discretization of Multiple Continuous Variables}
\label{DMC}
If there are multiple continuous variables in a Bayesian network, we iterate the one-variable discretization method discussed above for all continuous variables. While discretizing a continuous variable, other continuous variables must be discretized, either by a prediscretization that was done before the first iteration or by the discretization result of the latest iteration. The prediscretization can be done by equal-width discretization, which is defined as follows:
\begin{equation}
M_X =  \{ min_X, min_X + \delta, min_X + 2\delta, \ldots, \delta, max_X \},
\end{equation}
where $min_X$ and $max_X$ are minimal and maximal values of $D_X$, respectively, $\delta =  (max_X - min_X)/k$, and $k$ is the desired number of intervals after equal-width discretization. $k$ is same for all continuous variables and is set to be median value of all discrete variables' cardinalities. After prediscretization, we iterate the one-variable discretization on each continuous variable in the following order: from the continuous variable with highest topological order (leaves) to the continuous variable with lowest topological order (root). We call one such series of discretizations as a cycle. The advange of the order is that, for the first cycle of iteration, we can use less number of unsupervised discretization result. For example, in the right graph of Figure 2, assume $S_2$ is the only discrete variable. If we begin the iteration with $P_1$, then the discretization of $P_1$ will involve the prediscretization results of both $P_2$ and $X$. However, if we begin the iteration with $C_1$, then the discretization of $C_1$ will only involve the prediscretization result of $X$.
